\documentclass[12pt]{article}
\usepackage{fullpage,enumitem,amsmath,amssymb,graphicx, enumerate}

\title{18-703-modern-algebra-spring-2013 Final Exam Answers}
\author{Amauel Tewodros Getachew}

\begin{document}
  \maketitle
  \begin{center}

  \vspace{-0.3in}

  \end{center}


  \noindent
  \rule{\linewidth}{0.4pt}
  
  \section*{Problem 1}

  \begin{enumerate}[(i)]
    \item Give the definition of a group.  
    
    \noindent A group is a set $G$ along with a binary operation $(\cdot) : G \mapsto G$ such that the following three properties are satisfied:
    \begin{enumerate}
        \item \textit{Associativity}: If $a, b, c \in G$, then $(a \cdot b)\cdot c = a \cdot (b \cdot c)$.
        \item \textit{Existence of Identity}: There is an element $e$ of $G$ such that for every $a \in G$, $e \cdot a = a \cdot e =  a.$
        \item \textit{Existence of Inverse}: For each element $a \in G$, there is an element $b = a^{-1} \in G$ such that $a \cdot b = e$.
    \end{enumerate}

    \item Give the definition of an automorphism of groups. 
    
    \noindent An automorphism $\varphi$ of a group $G$ is an injective mapping from $G$ to itself such that for any $a, b \in G$, $\varphi(a \cdot b) = \varphi(a) \cdot\varphi(b).$

    \item Give the definition of $D_n$, the dihedral group. 

    \noindent $D_n$ is the group of rota-reflections of a regular $n-$gon with distinguishable vertices. Mathematically, 
    $$D_n := \{r^is^j : r^n = 1, s^2 = 1, rs = sr^{-1}\}.$$

    \item Give the definition of an ideal. 

    \noindent An Ideal $I$ is a sub-ring of a ring $R$ such that for every $r \in  R$, $rI \subseteq I$ and $Ir \subseteq I.$

    \item  Give the definition of a principal ideal domain.

    \noindent A principal ideal domain (PID) is an integral domain $R$ in which every ideal is generated by a single memeber. Mathematically, if $I \unlhd R$, then $I = (a) =  \{ra : r     \in R\}$ for some $a \in R$.


    \item Give the definition of a unique factorisation domain.

    \noindent A unique factorsation domain (UFD) is an integral domain $R$ in which every element $a$ can be expressed uniquely as a product of irreducibles in $R$ upto multiplication by units in $R$. Mathematically, if $p_i, q_i$ is irreducible in $R$, and $a = p_1 \cdots p_r = q_1 \cdots q_s$ then $r = s$ and $p_i = u_iq_i$ where $u_i$ is a unit in $R.$ 
    
  \end{enumerate}
\newcommand{\brk}[1]{\langle #1 \rangle}
  \section*{Problem 2}

  \begin{enumerate}[(i)]
    \item Let $G$ be a group and let $\sim$ be the relation $g_1 \sim g_2$ if there is an element $h \in G$ such that $g_1 = hg_2h^{-1}$. Show that $\sim$ is an equivalence relation.

    \noindent
    \begin{enumerate}
        \item \textit{Reflexive}: $a = aaa^{-1} = a$, thus $a \sim a$.
        \item \textit{Symmetric}: If $g_1 = hg_2h^{-1}$ then, $h^{-1} g_1 h =  g_2$,  which implies $g_1 \sim g_2 \implies g_2 \sim g_1$.
        \item \textit{Transitive}: If $g_1 = h_1g_2h_2^{-1}$ and $g_2 = h_2g_3h_2^{-1}$  then, $g_1 = h_1 h_2 g_3 h_2^{-1}h_1^{-1} =  h_3g_3h_3^{-1}$, where $h_3 = h_1h_2$.
    \end{enumerate}

    \item If $G = S_5$ then identify the equivalence classes.

    \noindent Let $\overline{\sigma}$ be the equivalence class that contains $\sigma$. To list all the equivalence classes of $\sim$, we use the following theorem.
    \newtheorem{thm}{Theorem}
    \begin{thm}
        If $\sigma = \prod_i (a_{i, 1}, \dots, a_{i, n_i}), \tau \in S_n$ then $\tau \sigma \tau^{-1} = \prod_i (\tau(a_{i, 1}), \dots, \tau(a_{i, n_i}))$. In particular,  $\sigma_1 \sim \sigma_2$, if and only if $\sigma_1$ and $\sigma_2$ have the same types.
    \end{thm}
    Therefore, the equivalence classes of $S_5$ are the following, 
     \begin{enumerate}[(1)]
         \item $\overline{1} = \{1\}$.
         \item $\overline{(1,2)} := \{\sigma: \mathrm{type}(\sigma) = (2, 1, 1, 1)\}$
         \item $\overline{(1,2)(3,4)} := \{\sigma: \mathrm{type}(\sigma) = (2, 2, 1)\}$
         \item $\overline{(1,2,3)} := \{\sigma: \mathrm{type}(\sigma) = (3, 1, 1)\}$
         \item $\overline{(1,2,3), (4, 5)} := \{\sigma: \mathrm{type}(\sigma) = (3, 2)\}$
        \item $\overline{(1,2,3,4)} := \{\sigma: \mathrm{type}(\sigma) = (4, 1)\}$
        \item $\overline{(1,2,3,4,5)} := \{\sigma: \mathrm{type}(\sigma) = (5)\}$
         
     \end{enumerate} 
    
  \end{enumerate}

    \newcommand{\Z}[1]{\mathbb{Z}/{#1}\mathbb{Z}}
  \section*{Problem 3}
  Classify all groups of order at most ten.
  

     \noindent We will use fundamental theorem of finite abelian groups to identify abelian groups. Let $|G| = n$
     \begin{itemize}
         \item If $n < 10$ is a prime, then $G$ can not have a proper subgroup other than the trivial sub-group and therefore it is cyclic. Hence, $G \cong \mathbb{Z}/n\mathbb{Z}$ for $n \in \{2, 3, 5, 7\}$
         \item If $n = 4$, by Lagrange's theorem, $a \neq e \in G$ implies $|a| \in \{2, 4\}$. If all three non-identity elements are of order $2$, then $G \cong V_4$. If $G$ is cyclic, then $G \cong \mathbb{Z}/4\mathbb{Z}$. Since, $G$ can not have two distinct members of order $2$ and only one of order $4$, we are done.
         \item Let $n = 6$. If $G$ is abelian, then $G \cong \mathbb{Z}/6\mathbb{Z}$ or $\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/3\mathbb{Z}$. Let $G$ be non-abelian. All elements of $G$ can not be of order $2$, because that would mean $G$ is abelian. Similarly, we can't have two elements $a, b$, $a \neq b^{-1}$ of order $3$ because then $G = \{1, a, a^2, b, b^2, ab\}$ in which case $(ab)^2 = b^2a^2 = e$ or $b^2 = b^{-1} = a$, a contradiction. Therefore, the only members of $G$ of order three are $a$ and $a^{-1}$ and $G$ is isomorphic to $S_3$. 
         \item Similarly, if $n = 10$, if $G$ is abelian, then $G \cong \Z{2} \times \Z{5}$ or $G \cong \Z{10}$. If $G$ is non-abelian, then $G \cong D_5$.
         \item If $n = 9$ and $G$ is abelian, $G \cong  \Z{9} $ or $G \cong \Z{3} \times \Z{3}$. If $G$ is non-abelian, then $G$ is not cyclic and there force contains $3$ cyclic sub-groups. Since $3$ is prime, two sub-groups have the trivial sub-groups as intersection. WLOG, let $\langle a\rangle, \langle b\rangle, \langle c\rangle, \langle d\rangle$ be the three subgroups of $G$. Then $ab$ can not be $e, a^{\pm 1}, b^{\pm 1}$. WLOG, let $ab = c$. This implies $ab = c$, $ac = d$ and $ad = b$. If $ab = ba$, then $ac = a^2 b = aba = ca$ and $ad = a^2ca = aca = da$, which implies $a \in Z(G)$ making $G$ commutative. Thus $ba = d$. But then $ad = b = a^2d = a^2ba = aca = da$ and by similar argument as above, $G$ becomes abelian. Thus there is no non-abelian group of order $9$.

        
         \item Let $n = 8$. If $G$ is abelian, then $ G $ is isomorphic to either $\Z{8}$, $\Z{4} \times \Z{2}$ or $\Z{2} \times \Z{2} \times \Z{2}$. If $G$ is non-abelian, by Lagrange's theorem, then there is at least on element $a$ of order $4$. If $\langle a \rangle$ is cycle of order $4$, and if all elements $b \in G - \langle a \rangle$ have order $2$, then $G \cong D_4$. Let $G$ contain two elements $a, b$ of order $4$. If $\brk{a} \cap \brk{b} = \{1\}$, then $ab = ba $ is an element of order $2$. But $e = abab = aabb = a^2b^2 \implies a^2 = b^2$. Thus $\brk{a} \cap \brk{b} = \{1, a^2\}$ since $a^{\pm 1}$ is a generator of $\brk{a}$. We know $ab, ba \in G - \brk{a} - \brk{b}$. Since $a^2 = b^2$, $aabb = e$ or $ab = a^3b^3 = (ba)^{-1}$. Thus $G\cong Q_8$. 
    \end{itemize}

\section*{Problem 4}
\begin{enumerate}[(i)]
    \item State the second isomorphism theorem.

    Let $G$ be a group and $H \leq G$ and $K \unlhd G$. Then, 

    $$\dfrac{HK}{K} \cong \dfrac{H}{H \cap K}$$

    \item Prove the second isomorphism theorem.

    Define a mapping $\phi: H \to HK/K$, as 
    $$\phi(h) = hK.$$

    Note that $\phi$ is surjective because if $a = hK \in HK/K$, then $\phi(h) = a.$ If $a, b \in H$, then $\phi(ab) = abK = aK\cdot bK = \phi(a)\phi(b)$. Thus $\phi$ is a homomorphism. Now, 
    $\ker \phi = \{h \in H: hK = K\} = \{h \in H: h \in K\} = H \cap K$. By the first Isomorphism theorem, the theorem follows.
    \end{enumerate}

    \section*{Problem 5}

    \begin{enumerate}[(i)]
        \item State Sylow’s theorems. 

        \begin{enumerate}
            \item \textit{First Sylow Theorem}: Let $n$ be the order of a group $G$ and $n = p^am$ where $p$ does not divide $m$. Then there is a subgroup of $G$ with order $p^a$ known as a Sylow $p$-group.
            \item \textit{Second Sylow Theorem}: If $P$ and $Q$ are two Sylow $p$-subgroups of $G$, then $P$ and $Q$ are conjugates of each other.

            \item \textit{Third Sylow Theorem}: If $n_p$ is the number of Sylow $p$-subgroups of $G$, then $n_p \equiv 1 \ \mathrm{mod}\  p.$
        \end{enumerate}

        \item Let $G$ be a group of order $pqr$, where $p$, $q$ and $r$ are distinct primes. Show that $G$ is not simple.

        WLOG, let $p < q < r$. By the third Sylow theorem, $n_r = 1 + kr$ for some $k > 0$ by assumption. Since $n_r > r, p, q$, $n_r | pqr$ and $n_r \nmid r$, $n_r = pq$. However, this means there are $pq(r-1)$ distinct elements in the Sylow $r-$group of $G$. Let $n_p = 1 + p$, and $n_q = 1 + q$, yielding $(p - 1)(p + 1) = p^2 - 1$ and $(q-1)(q+1) = (q^2 - 1)$ distinct elements (resp.) in the Sylow $p$-subgroups and Sylow $q$-subgroups (resp.). Thus we have

        $$pqr \geq pqr - pq + p^2 + q^2 -1.$$
        Clearly, $q^2 > pq  - p^2 = p(q - p) + 2$, yielding a contradiction and thus one of $n_p, n_q$ and $n_r$ is $1$.
    \end{enumerate}


\section*{Problem 6}
\begin{enumerate}[(i)]
    \item If the prime ideal $P$ contains the product $IJ$ of two ideals then prove that $P$ contains either $I$ or $J$.
    
    If $J \subseteq P$, there is nothing to prove, so let $J \nsubseteq P$. There is an element $j \in J$ not in $P$. We know $\{ij : i \in I\} \subseteq IJ \subseteq P$. Since $P$ is prime, this means $I \subseteq P.$ 
    \item Exhibit a natural bijection between the prime ideals of $R/IJ$ and $R/I \cap J$.

    Let $S_G$ be the collection of prime ideals in the group $G$. I claim that the mapping $\pi: S_{R/IJ} \to S_{R/I\cap J}$ defined by
    $$\pi(P/IJ) = P/I\cap J$$
    is a bijection. By (i), if $IJ \subseteq P \in S_{R}$, then $I \cap J \subseteq P.$ Therefore, $\pi$ is defined on the whole of $S_{R/IJ}.$ It remains to prove if $P$ is a prime ideal that contains $I \cap J$, then it should also contain $IJ$. This follows from noting that if $i \in I$ and $j \in J$, then $ij \in I \cap J$ and all finite sums of the form $\sum ij \in I \cap J$, implying $IJ \subseteq I \cap J$.
    \item Give an example of a ring $R$, and ideals $I$ and $J$ such that $IJ$ and $I \cap J$ are different.

    Consider the ideals $I =  \brk{2}$ and $J = \brk{4}$ in the ring $R = \mathbb{Z}.$ $IJ \subseteq \brk{8} \subset \brk{4} = I \cap J.$
\end{enumerate}

\section*{Problem 7}

Does every UFD $R$, which is not a field, contain infinitely many irreducible elements which are pairwise not associates? If your answer is yes then prove it and if no then give an example.\\ 


\noindent If $R$ is a UFD and not a field, this means it has infinite number of elements because a UFD is an integral domain by definition. Suppose $R$ has finitely many irreducible elements $p_1,  \dots, p_n$ and a unit $u$. The element $a = p_1 \cdots p_n + u$ is not divisible by any of the $p_i$, thus there is at least one irreducible element $p_{n+1}$ in the factorization of $a$.  By induction on $n$, it follows that $R$ contains an infinite number of irreducibles.

\section*{Problem 8}

Give an example of an integral domain such that every element of $R$ can be factored into irreducibles and yet $R$ is not a UFD.
\\

\noindent $R = \mathbb{Z}[\sqrt{-5}]$ is an integral domain that is not a UFD. To show that $6$ can be written as a product of different pairs of irreducibles, as $6 = 2\cdot3$ and $6 = (1 + \sqrt{-5})(1 - \sqrt{-5})$. We prove that $2, 3, 1 \pm \sqrt{-5}$ are irreducibles in $R$. To do that, we define a function(norm) $N: R \mapsto \mathbb{Z}$ as $N(a + b\sqrt{-5}) = a^2 + 5b^2.$ It is clear that $N(zw) = N(z)N(w).$ $N(2) = 4= 2\cdot 2$. Since $N(a +  b\sqrt{-5}) = a^2 + 5b^2 \neq 2$ for $a, b \in \mathbb{Z}$, $2$ must be irreducible. Similarly, $3$ and $1 \pm \sqrt{-5}$ are irreducible in $R$. Thus $R$ is not a UFD. 


\section*{Problem 9}
\begin{enumerate} [(i)]
    \item  Show that $\mathbb{Z}[i]$ is a Euclidean domain. \\ 

    \noindent Define an evaluation norm $v:\mathbb{Z}[i] \mapsto \mathbb{N} \cup \{0\}$ as $N(a + bi) = a^2 + b^2.$ Clearly, $v (0) = 0$ and $v(zw) = zw\overline{zw} = z\overline{z}w\overline{w} = v(z)v(w)$. Now we prove that if  $0 \neq z, w \in \mathbb{Z}[i]$, then $z = qw + r$ such that $v(w) > v(r) \geq 0.$  Let $x + yi = z/w$ and let $p + si$ be an element of $\mathbb{Z}[i]$ such that $|x - p| \leq 1/2$ and  $|y - s| \leq 1/2$. If $r = z - w(p + si)$, then
    \begin{eqnarray*}
        v(r) & = & v(z - w(p + qi)) \\
         & = & z - w(p + qi)\overline{(z - w(p + qi))}\\
         & = & w(z/w - (p + qi))\overline{w(z/w - (p + qi)}\\
         & = & w\overline{w}(z/w - (p + qi)\overline{(z/w - (p + qi)}\\
         & \leq &v(w)(1/4  + 1/4)\\
         & < & v(w).
    \end{eqnarray*}

    This proves  $\mathbb{Z}[i]$ is a Euclidean domain.

    \item  Is $6 - i$ prime in $\mathbb{Z}[i]$?

    Since $v(zw) = v(z)v(w)$, if $z \mid 6 - i$, $v(z) \mid v(6 - i) = 37$. But $37$ is a prime number and it's only divisors are $1$ and itself, making $6 - i$ irreducible. Since $\mathbb{Z}[i]$ is Euclidean domain, and therefore PID, $6 - i$ is then prime.

    \newcommand{\bb}[2]{\mathbb{#1}_{#2}}
    \section*{Problem 10}
    Write down all irreducible polynomials of degree 2 over the field $\bb{F}{5}$.\\

    \noindent Let $p(x) = ax^2 + bx + c, a\neq 0, b, c \in \bb{F}{5}.$ We consider two cases: \textit{Case 1}: $b = 0$. Substituting, $x = \pm 1$ and $x = \pm2$ in $p(x)$, we obtain $a \neq \pm c$. Hence, the polynomials $x^2 \pm 2$ and their associates are irreducible. \textit{Case 2}: if $b \neq 0$, we obtain $a + b + c \neq 0, -b, \pm 2b$, leaving only $a + b + c = b \implies a = -c$. In this case, the polynomial we need to investigate has the form $ax^2 + bx - a = a(x^2 + a^{-1}bx - 1)$. This implies $p(x)$ is irreducible iff $x^2 + b'x - 1$ is irreducible for $b' \neq 0.$ Considering the latter, case by case, we obtain $x^2 \pm2x -1 $ is irreducible. Hence The irreducible polynomials (upto multiplication by units) over the field $\bb{F}{5}$ are $\{ x^2 \pm  2, x^2 \pm 2x - 1\}$

\end{enumerate}

\section*{Problem 11}
\begin{enumerate}[(i)]
    \item State Gauss’ Lemma and Eisenstein’s criteria.\\
    
    \begin{itemize}
        \item \textit{Gauss' Lemma}: Let $D$ be an integral domain and let $F$ be its field of fraction. If $p(x)$ is a monic polynomial in $D[x]$ and it can be factorized in to two polynomials $f(x), g(x)$ in $F[x]$ as $p(x) = f(x)g(x)$, then $f(x)= u(x)v(x)$ such that $u(x), v(x) \in D[x]$ and $\deg f(x) = \deg u(x)$ and $\deg g(x) = \deg v(x).$

        \item \textit{Eisenstein's Criterion}: Let $p(x) = \sum_i a_ix^i \in \mathbb{Z}[x]$ and let $p$ be a prime. If $p \mid a_i$ for $0 \leq i < n$, $p \nmid a_n$ and $p^2 \nmid a_0$, then $p(x)$ is irreducible in $\mathbb{Z}[x]$ and hence in $\mathbb{Q}[x].$
    \end{itemize}
    \item Show that the polynomial $1 + x^3 + x^6 \in \mathbb{Q}[x]$ is irreducible (Hint: try a substitution.)\\

    \noindent Let $p(x) = 1 + x + x^2.$ The given polynomial is irreducible iff $p(x)$ is irreducible in $\mathbb{Q}[x].$ But $p(x)$ is irreducible if $p(x+1) = x^2 + 3x + 3$ is irreducible which it is by Eisenstein's criterion stated in (i) by taking $p = 3.$

    \item Show that the polynomial $1 - t^2 + t^5$ is irreducible over $\mathbb{Q}$ (Hint: consider the ring $\mathbb{F}_{2}[t]$.)\\

    \noindent First, we observe that if a monic polynomial is not irreducible in $\mathbb{Q}[x]$, then it is clearly not irreducible in $\mathbb{F}_p(x)$. To show that let $p(x)$ factorize into $p_1(x) \cdots p_n(x)$ in $\mathbb{Z}[x]$. Then $p(x) + \brk{p} = \big(\prod_i p_i(x) \big) + \brk{p} = \prod_i (p_i(x) + \brk{p}) \in \mathbb{F}_p(x)$. Hence, by contra-positive, $p(x)$ is irreducible in $\mathbb{Q}[x]$ if it is irreducible in $\mathbb{F}_p[x]$. Taking the special case, $p = 2$, $f(x) = 1 - x^2 + x^5 \neq 0$ for $x \in \{\pm 1, 0\}.$ Hence, $f(t)$ must be irreducible in $\mathbb{Q}[t].$
    

\end{enumerate}



\end{document}
